CF Registry Analysis

### 2023-12-13 Christine Chan/CF Registry/cf_registry_analysis.qmd
corrected numbers for people with >= 3 year gaps

```{r}
# I can't think of a good tidyverse way to do this, so trying it myself
dfs <- annual %>% select(eDWID, ReviewYear, cfrd_status_annual)
dfs <- split.data.frame(dfs, dfs$eDWID)
# For each ID, test whether they follow the pattern
fit_pattern <- lapply(dfs, function(d) {
  r <- rle(as.character(d$cfrd_status_annual))
  # Check for CFRD+, CFRD-, CFRD+ pattern
  # Can have NAs on either side of the CFRD- as well, so
  # CFRD+, CFRD-, CFRD+ OR CFRD+, NA, CFRD-, CFRD+ OR CFRD+, CFRD-, NA, CFRD+
  # OR CFRD+, NA,CFRD-, NA,CFRD+
  if (
    grepl(
      paste("CFRD\\+,CFRD\\-,CFRD\\+|", "CFRD\\+,NA,CFRD\\-,CFRD\\+|",
        "CFRD\\+,CFRD\\-,NA,CFRD\\+|", "CFRD\\+,NA,CFRD\\-,NA,CFRD\\+",
        sep = "", collapse = ""
      ),
      paste(r$values, collapse = ",")
    )) {
    return(unique(d$eDWID))
  } else {
    return(NA)
  }
})
fit_pattern = fit_pattern[!is.na(fit_pattern)]
# Filter out those that don't follow the pattern, calculate largest gaps 
# between CFRD+ diagnoses
largest_gap = annual %>% 
  filter(eDWID %in% names(t)) %>% 
  select(eDWID,ReviewYear,cfrd_status_annual) %>%
  group_by(eDWID) %>%
  summarise(largest_gap = max(diff(ReviewYear)))
```

There were a total of `r nrow(largest_gap)` partipants who had a diagnosis of CFRD+ followed by at least one CFRD-, followed again by a CFRD+ diagnosis. For each person, we calculated the largest gap between CFRD+ diagnoses.

```{r}
kable(table(largest_gap$largest_gap),
      col.names = c("Years between CFRD+","n"))
```

>>>>

```{r}
# I can't think of a good tidyverse way to do this, so trying it myself
dfs <- annual %>% select(eDWID, ReviewYear, cfrd_status_annual)
dfs <- split.data.frame(dfs, dfs$eDWID)
# For each ID, test whether they follow the pattern
fit_pattern <- lapply(dfs, function(d) {
  r <- rle(as.character(d$cfrd_status_annual))
  # Check for CFRD+, CFRD-, CFRD+ pattern
  # Can have NAs on either side of the CFRD- as well, so
  # CFRD+, CFRD-, CFRD+ OR CFRD+, NA, CFRD-, CFRD+ OR CFRD+, CFRD-, NA, CFRD+
  # OR CFRD+, NA,CFRD-, NA,CFRD+
  if (
    grepl(
      paste("CFRD\\+,CFRD\\-,CFRD\\+|", "CFRD\\+,NA,CFRD\\-,CFRD\\+|",
        "CFRD\\+,CFRD\\-,NA,CFRD\\+|", "CFRD\\+,NA,CFRD\\-,NA,CFRD\\+",
        sep = "", collapse = ""
      ),
      paste(r$values, collapse = ",")
    )) {
    return(unique(d$eDWID))
  } else {
    return(NA)
  }
})
fit_pattern = fit_pattern[!is.na(fit_pattern)]
# Filter out those that don't follow the pattern, calculate largest gaps 
# between CFRD+ diagnoses
largest_gap = annual %>% 
  filter(eDWID %in% names(fit_pattern),cfrd_status_annual=="CFRD+") %>% 
  select(eDWID,ReviewYear,cfrd_status_annual) %>%
  group_by(eDWID) %>%
  summarise(largest_gap = max(diff(ReviewYear))-1)
largest_gap = data.frame(table(largest_gap$largest_gap))
colnames(largest_gap) = c("Years between CFRD+","n")
```

There were a total of `r sum(largest_gap$n)` participants who had a diagnosis of CFRD+ followed by at least one CFRD-, followed again by a CFRD+ diagnosis. For each person, we calculated the largest gap between CFRD+ diagnoses. A total of `r sum(largest_gap$n[as.numeric(largest_gap[,1])>=3])` people had a gap $\geq$ 3 years.

```{r}
kable(largest_gap)
```
